Use of the gmse_apply function

### 2021-07-30 notebook/cran_vignettes/SI2.Rmd
Update the vignette for Issue #64 to explain the need for a landscape reset in gmse_apply loops

>>>>

Replenishing crops after consumption
================================================================================

Unlike with the `gmse` function, `gmse_apply` does not automatically assume that crop production should be replenished after a single time step. The second layer of [the landscape](SI7.pdf) holds crop production on a cell. This will be depleted if resources consume crops on the landscape.

```{r}
sim_consume <- gmse_apply(land_dim_1 = 8, land_dim_2 = 8, 
                          res_consume = 0.02, get_res = "Full");
print(round(sim_consume$LAND[,,2], digits = 2));
```

If we run this for five time steps using a loop in `gmse_apply`, then resources will continue to deplete crops on the landscape.

```{r, eval = TRUE}
sim_old     <- gmse_apply(land_dim_1 = 8, land_dim_2 = 8, 
                          res_consume = 0.02, get_res = "Full");
for(time_step in 1:5){
    sim_new                 <- gmse_apply(get_res = "Full", old_list = sim_old);
    sim_old                 <- sim_new;
}
print(round(sim_old$LAND[,,2], digits = 2));
```

Notice that the amount of crops on each cell has decreased substantially after five time steps. To replenish the crops after every `repl` time step, we can use the following code.

```{r, eval = TRUE}
sim_old     <- gmse_apply(land_dim_1 = 8, land_dim_2 = 8, 
                          res_consume = 0.02, get_res = "Full");
repl        <- 1;
for(time_step in 1:5){
    sim_new                 <- gmse_apply(get_res = "Full", old_list = sim_old);
    if(time_step %% repl == 0){ # If remainder of time_step / repl is zero
        sim_new$LAND[,,2] <- 1;
    }
    sim_old                 <- sim_new;
}
print(round(sim_old$LAND[,,2], digits = 2));
```

Now with the crop on the landscape replenishing every time step, each new time step starts with the landscape crop values set to 1. This is likely to be critical if simulating resources that must consume a certain amount to survive (`consume_surv > 0`) or reproduce (`consume_repr > 0`), and `gmse_apply` thereby provides some flexibility in terms of how frequently (and how much) landscape values change from one time step to the next.

### 2021-07-30 notebook/website_vignettes/SI2.Rmd
Update the vignette for Issue #64 to explain the need for a landscape reset in gmse_apply loops

>>>>

Replenishing crops after consumption
================================================================================

Unlike with the `gmse` function, `gmse_apply` does not automatically assume that crop production should be replenished after a single time step. The second layer of [the landscape](https://confoobio.github.io/gmse/articles/SI7.html#6-land) holds crop production on a cell. This will be depleted if resources consume crops on the landscape.

```{r}
sim_consume <- gmse_apply(land_dim_1 = 8, land_dim_2 = 8, 
                          res_consume = 0.02, get_res = "Full");
print(round(sim$LAND[,,2], digits = 2));
```

If we run this for five time steps using a loop in `gmse_apply`, then resources will continue to deplete crops on the landscape.

```{r, eval = TRUE}
sim_old     <- gmse_apply(land_dim_1 = 8, land_dim_2 = 8, 
                          res_consume = 0.02, get_res = "Full");
for(time_step in 1:5){
    sim_new                 <- gmse_apply(get_res = "Full", old_list = sim_old);
    sim_sum_4[time_step, 1] <- time_step;
    sim_old                 <- sim_new;
}
print(round(sim$LAND[,,2], digits = 2));
```

Notice that the amount of crops on each cell has decreased substantially after five time steps. To replenish the crops after every `repl` time step, we can use the following code.

```{r, eval = TRUE}
sim_old     <- gmse_apply(land_dim_1 = 8, land_dim_2 = 8, 
                          res_consume = 0.02, get_res = "Full");
repl        <- 1;
for(time_step in 1:5){
    sim_new                 <- gmse_apply(get_res = "Full", old_list = sim_old);
    sim_sum_4[time_step, 1] <- time_step;
    if(time_step %% repl == 0){ # If remainder of time_step / repl is zero
        sim_old$LAND[,,2] <- 1;
    }
    sim_old                 <- sim_new;
}
print(round(sim$LAND[,,2], digits = 2));
```

Now with the crop on the landscape replenishing every time step, consumption after five time steps comparable to consumption after a single time step. This is likely to be critical if simulating resources that must consume a certain amount to survive (`consume_surv > 0`) or reproduce (`consume_repr > 0`), and `gmse_apply` thereby provides some flexibility in terms of how frequently (and how much) landscape values change from one time step to the next.
